\texttt{vqtl}: An \texttt{R} package for Mean-Variance QTL Mapping

### 2018-07-12 revision/response.tex

% Ibáñez N, Varona L, Sorensen D, Noguera JL. A study of heterogeneity of environmental variance for slaughter weight in pigs. Animal. 2007;2:19-26.

% Sørensen P, de los Campos G, Morgante F, Mackay TFC, Sorensen D. Genetic Control of Environmental Variation of Two Quantitative Traits of Drosophila melanogaster Revealed by Whole-Genome Sequencing. Genetics. 2015;201(2):487-497. doi:10.1534/genetics.115.180273.

\section*{Reviewer 1 Comments}

\ReviewerQuestion{
  The authors mention ``in almost all traits of interest in human health and disease''.
  The detection of QTL has also been widely used in plant and animal populations.
}
\Response{
  The reviewer is quite correct that QTL mapping has been productively applied in plant an animal populations in addition to human populations.
  Rather than add references from plant and animal genetics to the introduction, we recognized that the introduction started unnecessarily broadly and therefore removed the first sentence.
  To address the reviewer's concern, however, we have added references to the following paragraph (where the heritability of phenotype variance is discussed) that rely heavily on studies of model organisms, livestock and crops.
}

### 2018-07-12 Package_vqt_Manuscript.tex
edits

Traditional quantitative trait locus (QTL) analyses have focused on discovering ``mean QTL'' (mQTL), regions of the genome where allelic variation drives heterogeneity of phenotype mean, while assuming that the residual variance, that is, the instrinsic stability or noisiness of the phenotype, is identical for every individual in the mapping population.
It has long been recognized, however, that the residual variance is itself heritable \WV{\citep{Falconer1965,Lynch1998}}{Do they definitely talk about this?}.
This phenomenon has been described theoretically \citep{Hill2004-uo,Hill2010}, demonstrated in inbred model organisms \WV{\citep{Sorensen2015}}{Seems a bit recent} and crops \citep{Yang2012-aw}, and exploited in livestock improvement efforts \citep{Mulder2008,Ibanez-Escriche2008-ie}.
%To help dissect the genetic basis, 
Correspondingly, several groups have proposed statistical methods for mapping QTL controling the extent of this residual variance, these sometimes termed ``variance QTL'' (vQTL) \citep{Pare2010,Ronnegard2011a,Ronnegard2012,Cao2014}\WV{\citep{Soave2017,Dumitrascu2018}}{add Englehardt, Soave?}.

>>>>

Traditional quantitative trait locus (QTL) analyses have focused on discovering ``mean QTL'' (mQTL), regions of the genome where allelic variation drives heterogeneity of phenotype mean, while assuming that the residual variance, that is, the intrinsic stability or noisiness of the phenotype, is identical for every individual in the mapping population.
It has long been recognized, however, that the residual variance is itself heritable \citep{Falconer1965,Lynch1998}.
This phenomenon has been described theoretically \citep{Hill2004-uo,Hill2010}, demonstrated in inbred model organisms \citep{Sorensen2015} and crops \citep{Yang2012-aw}, and exploited in livestock improvement efforts \citep{Mulder2008,Ibanez-Escriche2008-ie}.
%To help dissect the genetic basis, 
Correspondingly, several groups have proposed statistical methods for mapping QTL controling the extent of this residual variance, these sometimes termed ``variance QTL'' (vQTL) \citep{Pare2010,Ronnegard2011a,Ronnegard2012,Cao2014,Soave2017,Dumitrascu2018}.
